Although the location and size of small boats have been successfully identified, and the boats have been successfully but roughly classified into domestic recreational and fishing categories, more work is still needed to refine and improve them. In the future,

\begin{enumerate}
    
    \item in determining whether the boats are white or not, I created a function with RGB as the independent variable. I required the output of this function to be greater than a particular value (threshold). However, adjusting the parameters of this function can, in a certain sense, only be based on experience. So, does this threshold accurately identify the boat as being white in colour?
    
    \item if it is possible to roughly determine the type of small boat based on colour alone, is it possible that a dark coloured fishing boat is not detected on dark coloured seas? Would the number of fishing boats, in fact, then be greater?
    
    \item the satellite images capture only a moment in time during the year, are the fishing vessels operating slightly further out to sea and not captured by the satellite due to the nature of the fishing vessels?


    \item can data providers provide scholars with clear and close satellite imagery for free? Data is one of the triads of artificial intelligence and also the most overlooked factor. In fact, AI algorithms are highly dependent on data. It is as if the algorithms are always hungry, and all need a constant stream of data to feed their hunger. For object detection algorithms, poor image detail representation means less high-quality data. For the algorithm, fewer data often brings poor output results. Therefore, both the data used in building the model and the data used for detection should be kept at the highest level. Otherwise, training AI models loses its relative meaning.
    
    \item will Google Earth Pro provide a deep integration tool about the zoom scale in the future? Google Earth Pro provides very many images with details. However, Google Earth Pro does not offer similar integrated tools for zooming rulers as Google Maps does. If such a scaling environment were available, it would mean that every photo taken on Google Earth Pro would contain its scaling ratio. This means that we do not need to define a fixed zoom scale. It would be easy to know the object's length on each screenshot, regardless of whether the eye altitude is 200 meters or not. This leads to the fact that when some giant cargo ships or cruise ships need to be detected, we can reduce the scale to get an overall picture of the giant ship. When some tiny ships (e.g., a small ship under 5 meters in length) need to be inspected, we can zoom in to get the overall shape of the small ship.
    
    \item will small boats have a more precise classification in the future? Using colour to distinguish whether a boat is a recreational boat or a fishing boat may not be a solution that is acceptable to everyone. However, to solve this problem with a purely deep learning approach, one needs to train the data with all the types of boats that one wants to detect. However, doing the data classification and training in a realistic environment, i.e. Google Earth Pro, would be labour-intensive and costly. Furthermore, when looking for the classification category and the data under this category, is it possible to guarantee that the object‘s environment is the same as the object's environment under other categories due to the AI fairness principle? For example, is it possible to guarantee that the proportion of large cruise ships appearing on the beachside is the same as that of small recreational boats appearing on the beachside? The reason for this is that we do not want all large cruise ships to be offshore and all small recreational boats to be on the beach. If this is the case, the deep neural network does not need to know the contours or characteristics of the different boats. It just needs to analyse the background of the boats (i.e., the colour of the sea level, the colour of the beach, etc.) to predict whether a large cruise ship is likely to be a large cruise ship in the first place. One of the potential solutions to this problem is using computer simulation techniques to create CAD models of various ships. These CAD ships are then placed evenly into a variety of different background environments. Finally, these data are trained with deep neural networks, and then the trained models are put into real-life situations to detect some real ships.
    
    \item *will it be possible in the future to quickly scale up the algorithm to other regions? As well, will it be possible to analyse real-time satellite video in the future? Again, the key to expanding the algorithm to other regions and analysing real-time satellite video is to have fast and timely access to the data in the region. Frankly, it is whether the data providers can provide the data in the region. With real-time satellite video, it will be possible to get a better picture of maritime traffic in any area to monitor and control the carbon emissions of shipping in that area.
    
    \item is it possible to add more recognition objects, such as harbour and sea ripples, to prevent the recognition of harbour or sea ripples as small boats? The purpose of this is that once the algorithm can successfully identify the harbour or sea ripples, they will not be identified as small boats.
    
    \item can the timeframes be better? It is a question of optimisation, a trade-off question on cloud storage, a question of the algorithm's speed, and a question of the accuracy of the result. Besides, can the algorithm distinguish the same boat?
    
    \item Can we get a better idea of the type of engine on the boat? The connection of the ship is rightly allocated but still possible that it is difficult to know what type of engine or power is installed onboard. For this, a better understanding between the ship size and type and the levels of power needed is needed. This suggestion opens a new door of research.
\end{enumerate}
 
