\subsection{Energy Crisis, Energy Security and Climate Change}

The Intergovernmental Panel on Climate Change (IPCC) explains, in its latest report, that humans and nature are being pushed beyond their abilities to adapt due to the anthropogenic emissions caused by economic, industrial and societal activities~\cite{IPCC2022Portner}. Nowadays, carbon-intensive resources still comprise a large proportion of the energy system~\cite{IPCC2022Portner} – about 80\% in 2017~\cite{raturi2019renewables}. However, the share of electricity production from renewables increased from 20.8\% to 29.0\% between 1985 and 2020~\cite{BP2021bp}. Still, carbon emissions have not been reduced in line with the ambitions of the Paris Agreement, and it is predicted that in the next few years, the gains in carbon reduction due to the COVID-19 pandemic will be erased, faster than expected~\cite{WEO2021IEA}. However, even under all these pressures and projections, it is still possible for humanity to keep the global temperature below 1.5°C from pre-industrial levels by 2100 if substantial changes are made to the current energy systems.

On the other hand, energy security is an important part of the  strategies proposed by countries to support economic growth and provide essential services to their populations. Currently, nations deposit most of their energy security into fossil fuels while expanding their renewable power capacity. Fossil fuels and their conversion systems (e.g. internal combustion engines) permit operators to react quickly to changes in the energy demand (i.e. more control over energy deployment) while offering acceptable volumetric energy densities. However, heavy reliance on fossil fuels, coupled with the fuel’s geographical origin, is at the mercy of important price fluctuations due to geopolitical and logistical events, such as Russia’s invasion of Ukraine. These can disrupt energy systems and affect stability of nations and human livelihoods~\cite{bhattacharyya2009fossil,russiagas}. On the other hand, renewable energy production and distribution tend to lie within the country's boundaries. During the last few years, its price has been catching up with those of subsidised fossil fuels – with some specific examples already undercutting fossil fuel prices~\cite{IRENA2021Renewable}. In fact, from 1987 to 2015, the cost of oil and coal rose by approximately 36\% and 81\%, respectively and from 1989 to 2015, natural gas rose by approximately 53\%~\cite{BP2016bp}. More recently in March 2022, the UK experienced increases in natural gas to around £5.40/therm, a rise above 1,100\% from the price levels seen in 2021~\cite{T2022UKNatureGas}. Still, it is important to note that renewable energy variability and investment requirements are significant challenges to grid stability and energy security.

\subsection{Shipping Sector, Small Boat Fleet and Emission Inventory}
Shipping, the backbone of market globalisation, plays an important role in the carbon reduction of human activities since it moves around 90\% of all goods around the globe~\cite{walker2019environmental}. However, its reliance on fossil fuels, coupled with robust economic growth, saw total \ch{CO2} emissions grow from 962 Mt in 2012 to 1,056 Mt in 2018, representing more than 10\% of the total global transportation emissions ~\cite{IMO2021Fourth}. Further, if nothing is done in the sector, it was projected that by 2050 shipping \ch{CO2} emissions could grow to 1,500 Mt. In this light, the International Maritime Organisation (IMO) produced its ambitions to decarbonise international shipping~\cite{imo2018adoption} in 2018. However, this vision only covers international navigation composed of large vessels and does not consider the small boat fleet – vessels below 100 gross tonnages that tend to measure less than 24m in length~\cite{uk2021Operational}.

There are good reasons for this decision. First, the IMO focuses mainly on ships that navigate international waters or large ships performing domestic voyages. These vessels are required to have the Automatic Identification System (AIS) transponders for safe navigation. On the other hand, small boats tend not to have an AIS or GPS transponders, which makes the study of their movements more challenging. Second, they are typically registered and monitored by national and regional bodies, and the comprehensiveness of data depends on capital and human resources in addition to the infrastructure to maintain the registry. Third, small boats are a diverse segment of shipping and usage depends on the geographical location, type of activity, construction and operating costs, and accessibility to fuel or bunkering infrastructure. Similarly, engine providers are extensive, giving a broad range of fuel consumption curves and emissions.

Furthermore, fuel selection is equally diverse: petrol, diesel, petrol mixed with engine oil – mainly for two-stroke engines, ethanol and bio-fuels – or a mix of bio-fuel with different fossil fuels. Finally, on this matter, not all small boats are powered by an internal combustion engine. They can instead be powered by sail, battery-electric or paddles.

Nevertheless, under all these challenges, the small boat fleet can significantly estimate this shipping segment's emission footprint based on its activity. Emissions inventories aid our understanding of what measures must be taken to enable governments and the industry to start the road to full decarbonisation in a just and equitable way. Further, creating effective policies and regulations based on accurate emissions accounting can incentivise the use of energy-efficient technologies, electrification and scalable zero-emission fuels. Additionally, if countries want to meet their ambitious decarbonisation emissions targets, they cannot afford to ignore the role played in GHG by the small boat fleet.

Although it is possible to estimate emissions from large vessels using satellite data sent from the ship's transponder to be coupled with technical models~\cite{IMO2021Fourth}, small vessels depend on the national registration system. Their operation is typically assumed or captured by national fuel sales, which tend to be highly aggregated (e.g. ~\cite{sener2018balance}). Developed economies such as the UK tend to have a national registry of smaller vessels~\cite{uk2021registration} that provides a sense of their activity level and hence infer \ch{CO2} emissions.

However, in developing countries, it tends to be a mixed bag in terms of the level of precision and availability. For instance, in Mexico, only fishing vessels are counted in the registry ~\cite{Mexico2021RegisteredVessels}. Still, it is not easy to know where they are located and infer their activities. The remainder of the small boat categories are not registered. In all, Mexico does not have a regional \ch{CO2} inventory specialised in the small boat fleet; instead, they are aggregated as part of the \textit{maritime and fluvial navigation [1A3d]} class in the national annual emission inventory developed by the Instituto Nacional de Ecología y Cambio Climático (INECC)~\cite{inecc2020inventario} in a top-down approach recommended by the IPCC~\cite{eggleston20062006}. Therefore, quantifying and categorising the small boat fleet will allow a better precision of where and how the emissions are being emitted and will better understand the maritime emission inventory.

Observing shipping activity in the Gulf of California is essential due to its unique geographical location, conformation, and biophysical environment~\cite{LLUCHCOTA20071}~\cite{munguia2018ecological}~\cite{MARINONE2012133}. Furthermore, in the Gulf of California, there is the largest fishing state (Sonora) in Mexico~\cite{MELTZER2006222} and the most prominent sports fishing destination (Los Cabos, Baja)~\cite{hernandez2012economic}. Additionally, the region is one of the most protected areas in Mexico due to its diversity of flora and fauna; the area includes the upper part of the Gulf of California, Bahia Loreto and Bahia de los Angeles ~\cite{CNANP2022Atlas, SMARN2022Islas}. 



\subsection{Bringing Deep Learning to Small Ship Detection in Satellite Images}
Bringing deep learning, especially convolutional neural networks, to the field of satellite image recognition is essential. First, the technological barriers required by satellite image recognition gradually decrease with time. As the quality and quantity of global satellite images improve, it is possible to obtain the same or even better detection results with reduced parameters and the  complexity of convolutional neural networks. Second, satellite image recognition is not new. For example, scholars at the University of Texas at Austin have been using machine learning and remote sensing imagery to discover undersea shipwrecks successfully~\cite{character2021archaeologic}. However, finding submarine wrecks does not require algorithms to describe the location and size of the wreck very precisely, as opposed to identifying small boats and their physical characteristics. Therefore, in this study, accurately identifying and measuring the dimensions of small ships is a current challenge and an essential objective of this work.


\subsection{Contributions}
The contributions of this study are summarised as follows:
\begin{itemize}
    \item A purpose-built methodology for this work, BoatNet, was developed. Our research shows that BoatNet detects many small boats in low resolution, blurry satellite images with considerable noise levels. As a result, the precision of training can be up to 93.9\%, and detecting small boats in the Gulf of California can be up to 74.0\%.

    \item This work demonstrated that BoatNet could detect the length of small boats with a precision up to 99.0\%.

    \item BoatNet has allowed us to better understand small boat activity and physical characteristics. Based on this, it has been possible to answer questions about the composition of small boats in the Gulf of California. Regarding the authors' knowledge of the literature, this is a first but essential step in constructing a way to estimate the maritime carbon footprint of the small boat fleet.
\end{itemize}